---
title: "MAPpoly 2.0"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

## Background

MAPpoly 2.0 is an under development package to build genetic maps in diploids 
and polyploid interconnected populations. Some of the MAPpoly 2.0 features:

  - Mutli-population
  - Multi-allelic (from biallelic to complete informative markers)
  - Multi-ploidy (2, 4, 6 and any combination of those)

## What we have so far

The core function to re-estimate a genetic map in any of the situations listed 
above is already [implemented](https://github.com/mmollina/mappoly2/blob/main/src/est_hmm_map.cpp). However, there is a lot of functions that need to be implemented before we could release the package to the general public. In the next sections, I will present some functionality that are implemented in the current version.

### Merging maps from MAPpoly

```{r merging maps}
require(mappoly2)
require(mappoly)
require(tidyverse)
require(reshape2)
require(plotly)
source("~/repos/current_work/mappoly2/R/merge_mappoly_maps.R", echo=TRUE)
map_ch1_BExMG <- readRDS("~/repos/current_work/rose/fullsib_maps/BExMG/map_err_ch_1.rds")
map_ch1_SWxBE <- readRDS("~/repos/current_work/rose/fullsib_maps/SWxBE/map_err_ch_1.rds")
dat_BExMG <- readRDS("~/repos/current_work/rose/data/dat_BExMG.rds")
dat_SWxBE <- readRDS("~/repos/current_work/rose/data/dat_SWxBE.rds")
data.list <- list(BExMG = dat_BExMG,
                  SWxBE = dat_SWxBE)
map.list <- list(BExMG = map_ch1_BExMG,
                 SWxBE = map_ch1_SWxBE)
parents.mat <- matrix(c("BE", "MG", "SW", "BE"),
                      2, 2, byrow = TRUE,
                      dimnames = list(c("pop1", "pop2"), c("P1", "P2")))

states <- prepare_maps_to_merge(map.list, data.list, parents.mat)
restemp <- hmm_map_reconstruction(ploidy1 = states$ploidy$pl1,
                                  ploidy2 = states$ploidy$pl2,
                                  n.mrk = states$n.mrk,
                                  n.ind = states$n.ind,
                                  haplo = states$states,
                                  emit = states$emit,
                                  rf_vec = rep(0.01, states$n.mrk-1),
                                  verbose = FALSE,
                                  use_H0 = FALSE,
                                  tol = 1e-3)
dummy.map <- map_ch1_BExMG
dummy.map$maps[[1]]$seq.rf <- restemp[[2]]
dummy.map$info$mrk.names <- states$genome.pos$genome.pos$mrk
dummy.map$info$genome.pos <- states$genome.pos$genome.pos$geno.pos

l <- list(BExMG = map_ch1_BExMG,
        SWxBE = map_ch1_SWxBE,
        SWxBExMG = dummy.map)
```


```{r}
plot_map_list(l, col = c(mp_pal(3)))
```

```{r, eval=FALSE}
compare_single_maps(l)
```

## Simulations

```{r simulations}
require(mappoly2)
require(mappoly)
ploidy.vec <- c(4, 2, 6) #four parents
names(ploidy.vec) <- c("P1", "P2", "P3")
cross.mat <- matrix(c("P1","P2",
                      "P3","P1"), 
                    ncol = 2, byrow = T)
n.mrk <- c(50,50,50) #per parent
map.length <- 50 #in centimorgans
alleles <- list(P1 = c(0:3),
                P2 = c(2:5),
                P3 = c(0:5))
n.ind <- c(100, 100) #per cross

sim.cross <- simulate_multiple_crosses(ploidy.vec,
                                       cross.mat,
                                       n.ind,
                                       n.mrk,
                                       alleles,
                                       map.length)
sim.cross$
states <- states_to_visit(sim.cross)
restemp <- hmm_map_reconstruction(ploidy1 = states$ploidy$pl1,
                                  ploidy2 = states$ploidy$pl2,
                                  n.mrk = states$n.mrk,
                                  n.ind = states$n.ind,
                                  haplo = states$states,
                                  emit = states$emit,
                                  rf_vec = rep(0.01, states$n.mrk-1),
                                  verbose = FALSE,
                                  use_H0 = FALSE,
                                  tol = 1e-4)
plot(cumsum(imf_h(restemp[[2]])))
```
